### 2020-04-20 papers-vol-2.tex
updated titles vol 2

\insertmydocument{chapter}{What Optimistic Responses to Deep Disagreement get Right}{Scott F. Aikin}{pdfs/regular/2regularAikin.doc.pdf} % 2

@@

\insertmydocument{chapter}{Conceptual Analysis of an Argumentation using Argumentation Schemes and the Toulmin Model}{Marie Garnier, Patrick Saint-Dizier}{pdfs/regular/37regularGarnier.docx.pdf} % 37
\insertmydocument{chapter}{Representing Second-order Arguments with Adpositional Argumentation}{Federico Gobbo, Jean H.M. Wagemans}{pdfs/regular/39regularGobbo.doc.pdf} % 39

@@

\insertmydocument{chapter}{Auditory Arguments – Importance of Sound in an Argumentative Discourse}{Gabrijela Ki\v{s}i\v{c}ek}{pdfs/regular/60regularKisicek.docx.pdf} % 60

@@

\insertmydocument{chapter}{Strategic Manoeuvring with the Construction “We know that X” in Parliamentary Debates}{Matthijs Looij, Bertijn van der Steenhoven}{pdfs/regular/74regularLooij.docx.pdf} % 74

>>>>

\insertmydocument{chapter}{What Optimistic Responses to Deep Disagreement get Right (and Wrong)}{Scott F. Aikin}{pdfs/regular/2regularAikin.doc.pdf} % 2

@@

\insertmydocument{chapter}{Conceptual Analysis of an Argumentation: using Argumentation Schemes and the Toulmin Model}{Marie Garnier, Patrick Saint-Dizier}{pdfs/regular/37regularGarnier.docx.pdf} % 37
\insertmydocument{chapter}{Representing Second-order Arguments with Adpositional Argumentation (AdArg)}{Federico Gobbo, Jean H.M. Wagemans}{pdfs/regular/39regularGobbo.doc.pdf} % 39

@@

\insertmydocument{chapter}{Auditory Arguments – Importance of Sound in an Argumentative Discourse
(An Empirical Study)}{Gabrijela Ki\v{s}i\v{c}ek}{pdfs/regular/60regularKisicek.docx.pdf} % 60

@@

\insertmydocument{chapter}{Strategic Manoeuvring with the Construction “We (All) Know that X” in Parliamentary Debates}{Matthijs Looij, Bertijn van der Steenhoven}{pdfs/regular/74regularLooij.docx.pdf} % 74
